---
title: "Role-Playing with Robot Characters: Increasing User Engagement through Narrative and Gameplay Agency Data Analysis"
author: "Spencer Ng, Ting-Han Lin, You Li, Sarah Sebo"
date: "Last Updated 3/4/2024"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
theme: sandstone
highlight: tango
---

```{r, echo=FALSE, message= FALSE, warning= FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(lubridate)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ggExtra)
library(tidyr)
library(plyr)
library(plotly)
library(dplyr)
library(psych)
library(psycho)
library(tidyboot)
library(FactoMineR)
library(factoextra)
#library(devtools)
#install_github("kupietz/kableExtra")
library(kableExtra)
library(stringr)
library(formattable)
library(factoextra)
library(usmap)
library(alphaOutlier)
library(Rmisc)
library(mediation)
library(lme4)
library(lmerTest)
library(emmeans)
library(car)
library(mediation)
library(lsr)
library(rstatix)
library(fifer)

### Identify file path and names
result_data <- read.csv("rpr_anonymized_data.csv", header=T)
df <- result_data[2:nrow(result_data),] #get rid of one row below the header

# Convert values from str to int
df$Q5.1_1	<- strtoi(df$Q5.1_1)
df$Q5.1_2	<- strtoi(df$Q5.1_2)
df$Q5.1_3	<- strtoi(df$Q5.1_3)
df$Q5.1_4	<- strtoi(df$Q5.1_4)
df$Q5.1_5	<- strtoi(df$Q5.1_5)
df$Q5.1_6	<- strtoi(df$Q5.1_6)
df$Q5.1_7	<- strtoi(df$Q5.1_7)
df$Q5.1_8	<- strtoi(df$Q5.1_8)
df$Q5.1_9	<- strtoi(df$Q5.1_9)
df$Q6.1_2	<- strtoi(df$Q6.1_2)
df$Q8.3_4	<- strtoi(df$Q8.3_4)
df$Q8.5_4	<- strtoi(df$Q8.5_4)
df$Q9.1_1	<- strtoi(df$Q9.1_1)
df$Q9.1_2	<- strtoi(df$Q9.1_2)
df$Q9.1_3	<- strtoi(df$Q9.1_3)
df$lee.positive <- strtoi(df$lee.positive)
df$lee.negative <- strtoi(df$lee.negative)
df$lee.neutral <- strtoi(df$lee.neutral)
df$lee.positive.negative <- strtoi(df$lee.positive.negative)
df$jay.positive <- strtoi(df$jay.positive)
df$jay.negative <- strtoi(df$jay.negative)
df$jay.neutral <- strtoi(df$jay.neutral)
df$jay.positive.negative <- strtoi(df$jay.positive.negative)
df$overall.positive <- strtoi(df$overall.positive)
df$overall.ignored <- strtoi(df$overall.ignored)
df$overall.non_immersed <- strtoi(df$overall.non_immersed)

#continuous variables should not be factors
df$flow_avg <- as.numeric(df$flow_avg)
df$Q10.2_1	<- as.numeric(df$Q10.2_1) #role-playing experiences 
df$Q10.2_2	<- as.numeric(df$Q10.2_2) #experience playing cryptic puzzles
df$Q10.2_3	<- as.numeric(df$Q10.2_3) #experience interacting with robots 
df$Q10.2_4	<- as.numeric(df$Q10.2_4) #experience with programming
df$tipi_extraversion <- as.numeric(df$tipi_extraversion)
df$tipi_openness <- as.numeric(df$tipi_openness)
df$Jay..RoSAS.Warmth <- as.numeric(df$Jay..RoSAS.Warmth)
df$Lee..RoSAS.Warmth <- as.numeric(df$Lee..RoSAS.Warmth)
df$PENS..Autonomy <- as.numeric(df$PENS..Autonomy)
df$PENS..Presence.Immersion <- as.numeric(df$PENS..Presence.Immersion)
df$PENS..Relatedness <- as.numeric(df$PENS..Relatedness)
df$PENS..Competence <- as.numeric(df$PENS..Competence)
df$total_time_utterance <- as.numeric(df$total_time_utterance)
df$total_prompted_utterance <- as.numeric(df$total_prompted_utterance)
df$total_unprompted_utterance <- as.numeric(df$total_unprompted_utterance)

df$Q1.1[df$Q1.1 == "Control"] <- 1
df$Q1.1[df$Q1.1 == "Gameplay Agency"] <- 2
df$Q1.1[df$Q1.1 == "Narrative Agency"] <- 3

df$Q1.1 <- factor(
  df$Q1.1,
  levels = 1:3, 
  labels = c("Control", "Gameplay Agency", "Narrative Agency")
)

```


## 3.6.1 Short Flow State Scale: Challenge-Skill Balance

#### I felt like I was competent enough to meet the high demands of the situation. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_1", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_1)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_1-se, ymax=Q5.1_1+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_1,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_1,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_1 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_1 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_1, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Action-Awareness Merging

#### I did things spontaneously and automatically without having to think. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_2", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_2)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_2-se, ymax=Q5.1_2+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_2,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_2,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_2 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_2 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_2, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Clear Goals

#### I had a strong sense of what I wanted to do. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_3", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_3)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_3-se, ymax=Q5.1_3+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_3,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_3,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_3 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_3 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_3, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Unambiguous Feedback

#### I had a good idea while I was performing of how well I was doing. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_4", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_4)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_4-se, ymax=Q5.1_4+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_4,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_4,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_4 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_4 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_4, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Concentration on Task

#### I was completely focused on the task in hand. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_5", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_5)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_5-se, ymax=Q5.1_5+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_5,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_5,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_5 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_5 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_5, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Sense of Control

#### I had a feeling of total control over what I was doing. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_6", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_6)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_6-se, ymax=Q5.1_6+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_6,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_6,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_6 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_6 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_6, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Transformation of Time

#### The way time passed seemed to be different from normal. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_7", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_7)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_7-se, ymax=Q5.1_7+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_7,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_7,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_7 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_7 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_7, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Loss of self-consciousness

#### I was not concerned with how Agent Lee and Agent Jay  perceived me. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_8", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_8)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_8-se, ymax=Q5.1_8+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_8,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_8,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_8 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_8 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_8, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Autotelic Experience

#### The experience was extremely rewarding. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q5.1_9", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q5.1_9)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q5.1_9-se, ymax=Q5.1_9+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q5.1_9,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q5.1_9,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q5.1_9 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q5.1_9 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q5.1_9, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.1 Short Flow State Scale: Overall Flow Score

#### Overall Flow Score {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="flow_avg", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=flow_avg)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=flow_avg-se, ymax=flow_avg+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,5]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 5))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$flow_avg,
df['Q1.1'],
mean
)
sds <- aggregate(
df$flow_avg,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(flow_avg ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(flow_avg ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$flow_avg, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.2 Player Experience of Need Satisfaction: Autonomy

#### Autonomy {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="PENS..Autonomy", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=PENS..Autonomy)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=PENS..Autonomy-se, ymax=PENS..Autonomy+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$PENS..Autonomy,
df['Q1.1'],
mean
)
sds <- aggregate(
df$PENS..Autonomy,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(PENS..Autonomy ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(PENS..Autonomy ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$PENS..Autonomy, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.2 Player Experience of Need Satisfaction: Competence

#### Competence {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="PENS..Competence", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=PENS..Competence)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=PENS..Competence-se, ymax=PENS..Competence+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$PENS..Competence,
df['Q1.1'],
mean
)
sds <- aggregate(
df$PENS..Competence,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(PENS..Competence ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(PENS..Competence ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$PENS..Competence, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.2 Player Experience of Need Satisfaction: Relatedness

#### Relatedness {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="PENS..Relatedness", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=PENS..Relatedness)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=PENS..Relatedness-se, ymax=PENS..Relatedness+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$PENS..Relatedness,
df['Q1.1'],
mean
)
sds <- aggregate(
df$PENS..Relatedness,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(PENS..Relatedness ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(PENS..Relatedness ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$PENS..Relatedness, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.2 Player Experience of Need Satisfaction: Immersion

#### Immersion {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="PENS..Presence.Immersion", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=PENS..Presence.Immersion)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=PENS..Presence.Immersion-se, ymax=PENS..Presence.Immersion+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$PENS..Presence.Immersion,
df['Q1.1'],
mean
)
sds <- aggregate(
df$PENS..Presence.Immersion,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(PENS..Presence.Immersion ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(PENS..Presence.Immersion ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$PENS..Presence.Immersion, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.3 Player Social Perceptions: Awkward

#### Awkward {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q9.1_1", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q9.1_1)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q9.1_1-se, ymax=Q9.1_1+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q9.1_1,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q9.1_1,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q9.1_1 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q9.1_1 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q9.1_1, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.3 Player Social Perceptions: Vulnerable

#### Vulnerable {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q9.1_3", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q9.1_3)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q9.1_3-se, ymax=Q9.1_3+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q9.1_3,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q9.1_3,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q9.1_3 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q9.1_3 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q9.1_3, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.3 Player Social Perceptions: Watched

#### Watched {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q9.1_2", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q9.1_2)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q9.1_2-se, ymax=Q9.1_2+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q9.1_2,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q9.1_2,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q9.1_2 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q9.1_2 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q9.1_2, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.4 Robotic Social Attributes Scale: Advisor Robot's Warmth

#### Advisor Robot's Warmth {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Jay..RoSAS.Warmth", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Jay..RoSAS.Warmth)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Jay..RoSAS.Warmth-se, ymax=Jay..RoSAS.Warmth+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Jay..RoSAS.Warmth,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Jay..RoSAS.Warmth,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Jay..RoSAS.Warmth ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Jay..RoSAS.Warmth ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Jay..RoSAS.Warmth, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.4 Robotic Social Attributes Scale: Peer Robot's Warmth

#### Peer Robot's Warmth {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Lee..RoSAS.Warmth", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Lee..RoSAS.Warmth)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Lee..RoSAS.Warmth-se, ymax=Lee..RoSAS.Warmth+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Lee..RoSAS.Warmth,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Lee..RoSAS.Warmth,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Lee..RoSAS.Warmth ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Lee..RoSAS.Warmth ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Lee..RoSAS.Warmth, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.5 Additional Robot and Experience Perceptions: Advisor robot is actively engaged

#### Agent Jay was actively engaged with me during the experience. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q8.5_4", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q8.5_4)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q8.5_4-se, ymax=Q8.5_4+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q8.5_4,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q8.5_4,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q8.5_4 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q8.5_4 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q8.5_4, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.5 Additional Robot and Experience Perceptions: Peer robot is actively engaged

#### Agent Lee was actively engaged with me during the experience. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q8.3_4", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q8.3_4)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q8.3_4-se, ymax=Q8.3_4+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q8.3_4,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q8.3_4,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q8.3_4 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q8.3_4 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q8.3_4, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.5 Additional Robot and Experience Perceptions: Given the chance, I would participate in this experience in my free time.

#### Given the chance, I would participate in this experience in my free time. {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q6.1_2", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q6.1_2)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q6.1_2-se, ymax=Q6.1_2+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q6.1_2,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q6.1_2,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q6.1_2 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q6.1_2 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q6.1_2, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.6 Coded Free-Response: Peer Robot's Impression is Positive

#### Peer Robot's Impression is Positive {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="lee.positive", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=lee.positive)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=lee.positive-se, ymax=lee.positive+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$lee.positive,
df['Q1.1'],
mean
)
sds <- aggregate(
df$lee.positive,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$lee.positive == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$lee.positive == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$lee.positive == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$lee.positive == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$lee.positive == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$lee.positive == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("lee.positive = 1", "lee.positive = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Peer Robot's Impression is Negative

#### Peer Robot's Impression is Negative {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="lee.negative", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=lee.negative)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=lee.negative-se, ymax=lee.negative+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$lee.negative,
df['Q1.1'],
mean
)
sds <- aggregate(
df$lee.negative,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$lee.negative == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$lee.negative == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$lee.negative == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$lee.negative == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$lee.negative == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$lee.negative == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("lee.negative = 1", "lee.negative = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Peer Robot's Impression is Neutral

#### Peer Robot's Impression is Neutral {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="lee.neutral", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=lee.neutral)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=lee.neutral-se, ymax=lee.neutral+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$lee.neutral,
df['Q1.1'],
mean
)
sds <- aggregate(
df$lee.neutral,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$lee.neutral == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$lee.neutral == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$lee.neutral == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$lee.neutral == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$lee.neutral == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$lee.neutral == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("lee.neutral = 1", "lee.neutral = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Peer Robot's Impression is a Mixture of Positive and Negative Attributes

#### Peer Robot's Impression is a Mixture of Positive and Negative Attributes {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="lee.positive.negative", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=lee.positive.negative)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=lee.positive.negative-se, ymax=lee.positive.negative+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$lee.positive.negative,
df['Q1.1'],
mean
)
sds <- aggregate(
df$lee.positive.negative,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$lee.positive.negative == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$lee.positive.negative == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$lee.positive.negative == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$lee.positive.negative == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$lee.positive.negative == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$lee.positive.negative == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("lee.positive.negative = 1", "lee.positive.negative = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Advisor Robot's Impression is Positive

#### Advisor Robot's Impression is Positive {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="jay.positive", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=jay.positive)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=jay.positive-se, ymax=jay.positive+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$jay.positive,
df['Q1.1'],
mean
)
sds <- aggregate(
df$jay.positive,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$jay.positive == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$jay.positive == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$jay.positive == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$jay.positive == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$jay.positive == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$jay.positive == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("jay.positive = 1", "jay.positive = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Advisor's Robot's Impression is Negative

#### Advisor's Robot's Impression is Negative {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="jay.negative", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=jay.negative)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=jay.negative-se, ymax=jay.negative+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$jay.negative,
df['Q1.1'],
mean
)
sds <- aggregate(
df$jay.negative,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$jay.negative == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$jay.negative == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$jay.negative == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$jay.negative == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$jay.negative == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$jay.negative == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("jay.negative = 1", "jay.negative = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Advisor's Robot's Impression is Neutral

#### Advisor's Robot's Impression is Neutral {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="jay.neutral", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=jay.neutral)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=jay.neutral-se, ymax=jay.neutral+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$jay.neutral,
df['Q1.1'],
mean
)
sds <- aggregate(
df$jay.neutral,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$jay.neutral == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$jay.neutral == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$jay.neutral == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$jay.neutral == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$jay.neutral == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$jay.neutral == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("jay.neutral = 1", "jay.neutral = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Advisor Robot's Impression is a Mixture of Positive and Negative Attributes

#### Advisor Robot's Impression is a Mixture of Positive and Negative Attributes {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="jay.positive.negative", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=jay.positive.negative)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=jay.positive.negative-se, ymax=jay.positive.negative+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$jay.positive.negative,
df['Q1.1'],
mean
)
sds <- aggregate(
df$jay.positive.negative,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$jay.positive.negative == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$jay.positive.negative == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$jay.positive.negative == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$jay.positive.negative == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$jay.positive.negative == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$jay.positive.negative == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("jay.positive.negative = 1", "jay.positive.negative = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Feeling Positive About the Overall Experience

#### Feeling Positive About the Overall Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="overall.positive", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=overall.positive)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=overall.positive-se, ymax=overall.positive+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$overall.positive,
df['Q1.1'],
mean
)
sds <- aggregate(
df$overall.positive,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$overall.positive == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$overall.positive == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$overall.positive == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$overall.positive == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$overall.positive == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$overall.positive == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("overall.positive = 1", "overall.positive = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Feeling Ignored About the Overall Experience

#### Feeling Ignored About the Overall Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="overall.ignored", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=overall.ignored)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=overall.ignored-se, ymax=overall.ignored+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$overall.ignored,
df['Q1.1'],
mean
)
sds <- aggregate(
df$overall.ignored,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$overall.ignored == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$overall.ignored == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$overall.ignored == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$overall.ignored == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$overall.ignored == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$overall.ignored == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("overall.ignored = 1", "overall.ignored = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.6 Coded Free-Response: Feeling Not Immersed About the Overall Experience

#### Feeling Not Immersed About the Overall Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="overall.non_immersed", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=overall.non_immersed)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=overall.non_immersed-se, ymax=overall.non_immersed+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Proportion [0,1]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 1))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$overall.non_immersed,
df['Q1.1'],
mean
)
sds <- aggregate(
df$overall.non_immersed,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Chi Squared Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

new.matrix <- cbind(as.data.frame(
  c(nrow(df[df$overall.non_immersed == '1' & df$Q1.1 == "Control", ]), 
    nrow(df[df$overall.non_immersed == '1' & df$Q1.1 == "Gameplay Agency", ]),
    nrow(df[df$overall.non_immersed == '1' & df$Q1.1 == "Narrative Agency", ]))),
  as.data.frame(c(nrow(df[df$overall.non_immersed == '0' & df$Q1.1 == "Control", ]),
                  nrow(df[df$overall.non_immersed == '0' & df$Q1.1 == "Gameplay Agency", ]),
                  nrow(df[df$overall.non_immersed == '0' & df$Q1.1 == "Narrative Agency", ]))))

colnames(new.matrix) <- c("overall.non_immersed = 1", "overall.non_immersed = 0")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

chisq.test(
  new.matrix,
  correct=FALSE
)

chisq.post.hoc(new.matrix, control = "bonferroni", popsInRows  = TRUE)

```




## 3.6.7 Personality and Prior Experience: Extraversion

#### Extraversion {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="tipi_extraversion", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=tipi_extraversion)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=tipi_extraversion-se, ymax=tipi_extraversion+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$tipi_extraversion,
df['Q1.1'],
mean
)
sds <- aggregate(
df$tipi_extraversion,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(tipi_extraversion ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(tipi_extraversion ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$tipi_extraversion, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.7 Personality and Prior Experience: Openness

#### Openness {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="tipi_openness", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=tipi_openness)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=tipi_openness-se, ymax=tipi_openness+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$tipi_openness,
df['Q1.1'],
mean
)
sds <- aggregate(
df$tipi_openness,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(tipi_openness ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(tipi_openness ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$tipi_openness, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.7 Personality and Prior Experience: Role-Playing Experience

#### Role-Playing Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q10.2_1", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q10.2_1)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q10.2_1-se, ymax=Q10.2_1+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q10.2_1,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q10.2_1,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q10.2_1 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q10.2_1 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q10.2_1, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.7 Personality and Prior Experience: Cryptic Puzzle Experience

#### Cryptic Puzzle Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q10.2_2", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q10.2_2)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q10.2_2-se, ymax=Q10.2_2+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q10.2_2,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q10.2_2,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q10.2_2 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q10.2_2 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q10.2_2, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.7 Personality and Prior Experience: Robot Experience

#### Robot Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q10.2_3", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q10.2_3)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q10.2_3-se, ymax=Q10.2_3+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q10.2_3,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q10.2_3,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q10.2_3 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q10.2_3 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q10.2_3, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.7 Personality and Prior Experience: Programming Experience

#### Programming Experience {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="Q10.2_4", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=Q10.2_4)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=Q10.2_4-se, ymax=Q10.2_4+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [1,7]")+
theme_bw()+  
coord_cartesian(ylim = c(1, 7))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$Q10.2_4,
df['Q1.1'],
mean
)
sds <- aggregate(
df$Q10.2_4,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(Q10.2_4 ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(Q10.2_4 ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$Q10.2_4, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.8 Verbal Engagement: Prompted Utterances

#### Prompted Utterances {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="total_prompted_utterance", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=total_prompted_utterance)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=total_prompted_utterance-se, ymax=total_prompted_utterance+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [0,250]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 250))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$total_prompted_utterance,
df['Q1.1'],
mean
)
sds <- aggregate(
df$total_prompted_utterance,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(total_prompted_utterance ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(total_prompted_utterance ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$total_prompted_utterance, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.8 Verbal Engagement: Unprompted Utterances

#### Unprompted Utterances {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="total_unprompted_utterance", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=total_unprompted_utterance)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=total_unprompted_utterance-se, ymax=total_unprompted_utterance+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [0,250]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 250))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$total_unprompted_utterance,
df['Q1.1'],
mean
)
sds <- aggregate(
df$total_unprompted_utterance,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(total_unprompted_utterance ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(total_unprompted_utterance ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$total_unprompted_utterance, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```




## 3.6.8 Verbal Engagement: Combined Utterances

#### Combined Utterances {.tabset}

##### Plot

```{r, echo=FALSE, message= FALSE, warning= FALSE}

summarySE <- summarySE(df, measurevar="total_time_utterance", groupvars=c("Q1.1"))
plot <- ggplot(data=summarySE, aes(x=Q1.1, y=total_time_utterance)) +
geom_bar(position=position_dodge(), stat="identity", width=0.5, fill=c("#054C70","#05C3DE", "#b0e2ff")) +
geom_errorbar(aes(ymin=total_time_utterance-se, ymax=total_time_utterance+se),width=.2, position=position_dodge(.9)) +
xlab("Condition") + scale_y_continuous(expand = c(0, 0))+
ylab("Questionnaire Rating [0,250]")+
theme_bw()+  
coord_cartesian(ylim = c(0, 250))+
theme(axis.text = element_text(color="black", size = 12), axis.title.y = element_text(color="black", size = 15), 
axis.title.x = element_text(color="black", size = 15), axis.line.x = element_line(color="black", size = 0.25), axis.line.y = element_line(color="black", size = 0.25))+
theme(panel.background = element_rect(fill = "#FFFFFF", colour = "#FFFFFF", linetype = "solid"))
    
plot

```
<br>

**Mean and Standard deviation:**

```{r, echo=FALSE, message= FALSE, warning= FALSE}
# mean & stdev for all conditions

means <- aggregate(
df$total_time_utterance,
df['Q1.1'],
mean
)
sds <- aggregate(
df$total_time_utterance,
df['Q1.1'],
sd
)

new.matrix <- cbind(as.data.frame(means[2]), as.data.frame(sds[2]))
colnames(new.matrix) <- c("Mean", "Standard Deviation")
rownames(new.matrix) <- c("Control", "Gameplay Agency", "Narrative Agency")

kbl(new.matrix, digits = 3, align = c("l", "c", "c", "c")) %>% kable_classic() %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

##### Kruskal-Wallis Test

```{r, echo=FALSE, message= FALSE, warning= FALSE}

# Compute Kruskal-Wallis test
kruskal.test(total_time_utterance ~ Q1.1, data = df)

#Computer Kruskal-Wallis test effect size
kruskal_effsize(total_time_utterance ~ Q1.1, data = df) 

# Multiple pairwise-comparison between groups
my_pairwise_test <- pairwise.wilcox.test(df$total_time_utterance, df$Q1.1, p.adjust.method = "bonferroni")
my_pairwise_test

```

